Review for Production and Operations Management(2024)

### 2025-01-06 posts/Review/review.qmd
abortion add

---
title: "Review for Production and Operations Management(2024)"
date: 09/16/2024
date-modified: last-modified
date-format: full
categories: [Others]
#image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
---

>>>>

---
title: "Review for Production and Operations Management(2024)"
date: 09/16/2024
date-modified: last-modified
draft: true
date-format: full
categories: [Others]
#image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
---
